---
title: Markdown Primer
author: Jared P. Lander
date: May 9, 2018
output: html_document
---

# My First Section

We started a new section with a hashtag and this is the first paragraph in that section. Notice that the text will automatically wrap to the next line in the editor, but it still has the same line number. All text within the same line number is considered a single paragraph. Be aware that markdown is highly space sensitive.

Leaving a blank line starts a new paragraph. Remember, markdown is highly case sensitive. Adding a third sentence to fit in with antiquated rules of writing, even though JD Salinger would disagree.
If you don't leave a blank line, this sentence is still part of the same paragraph.

# New Section

You start a new section by leaving a blank line and starting the next line with a hashtag. No need to close the previous section, simply start a new section.

# Subsections

Creating subsections is just as easy, simply use two hashtags.

## First Subsection

We started a subsection within a section by using two hashtags. No need to do anything to the section itself.

## Another Subsection

Just like with sections, to start a new subsection simply start a line with two hashtags. No need to close the previous subsection.

# Back to Sections

We return to a level 1 section by starting a new one with a single hashtag. Again, no need to close previous sections or subsections.

# Formatting Text

_Emphasized Text_

__Strong Text__

___Emphasized and strong text___

`anything in backticks looks like computer code`

# Lists

## Unordered Lists

- Apple
    - Honeycrisp
    - Pinova
    - Granny Smith
    - Cortlandt
- Banana
- Orange
- Kiwi
- Durian
- Watermelon

## Ordered Lists

1. New York
1. New Jersey
1. Naples
1. Detroit
1. Philadelphia
1. Rome

a. Mushrooms
a. Sausage
a. Garlic

# Links

[My Website](http://www.jaredlander.com)

# R Time!!!!!!!!!!!

```{r}
1 + 1
```

```{r}
# this is a comment inside of R
x <- 3
x
```

```{r}
x*2
```

Let's give our chunks names.

```{r simple-code-ex}
x*3 + 7
```

Let's show the results of a chunk without seeing the code.

```{r another-example,echo=FALSE}
5*x + 4
```


